---
title: "Untitled"
output: html_document
date: "2024-08-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| **Type**       | **Name**                                                                    | **Note**          | **URL**                                                                                                                                    | **Reference**                                |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| Article        | Fast Evaluation of Study Designs for Spatially Explicit Capture–Recapture   | resource1_note    | <https://doi.org/10.1111/2041-210X.13239>                                                                                                  | {{ ref_textbib_efford-boulanger_2019 }}      |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| App/Program    | Secrdesign app 1.5                                                          | resource2_note    | <https://www.stats.otago.ac.nz/secrdesignapp/>                                                                                             | {{ ref_textbib_ref_efford-boulanger_2019  }} |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| App/Program    | Program SPACECAP                                                            | Removed from cran | <https://cran.r-project.org/web/packages/SPACECAP/index.html>                                                                              | {{ ref_textbib_gopalaswamy-et-al_2021 }}     |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
|                |                                                                             |                   |                                                                                                                                            |                                              |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| R package      | R package “oSCR”- “sim.SCR” function                                        | resource4_note    | <https://onlinelibrary.wiley.com/doi/10.1111/ecog.04551>                                                                                   | {{ ref_textbib_sutherland-et-al_2018}}       |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| R package      | R package “secr”                                                            | resource5_note    | Package info: <https://cran.r-project.org/web/packages/secr/index.html>                                                                    | {{ ref_textbib_efford_2024 }}                |
|                |                                                                             |                   |                                                                                                                                            |                                              |
|                |                                                                             |                   | Help forum: \<www.phidot.org\>                                                                                                             |                                              |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| resource6_type | resource6_name                                                              | resource6_note    | <https://science.uct.ac.za/seec/stats-toolbox-seminars-spatial-and-species-distribution-toolboxes/spatial-capture-recapture-scr-modelling> | resource6_ref                                |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
|                |                                                                             |                   |                                                                                                                                            |                                              |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
| App/Program    | DENSITY                                                                     | resource7_note    | resource7_url                                                                                                                              | resource7_ref                                |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+
|                |                                                                             |                   |                                                                                                                                            |                                              |
+----------------+-----------------------------------------------------------------------------+-------------------+--------------------------------------------------------------------------------------------------------------------------------------------+----------------------------------------------+

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
